### 2014-05-05 brains-protocol.tex
Fix missing fix of #meanings to #synonyms in protocol
Choose timebag evolution model
We use the chains with minimum 20 timebags per cluster, no quotes
excluded from previous timebags. This is the best
number-of-words/explanation-complexity ratio.

\begin{itemize}
    \item \textbf{Word frequency}: the frequency at which words appear in our dataset, \rk{add ref on why it's important}
    \item \textbf{Age of Acquisition}: the average age at which words are learned, obtained from~\citet{kuperman12},
    \item The average \textbf{Number of Phonemes} for all pronunciations of a word, obtained from the Carnegie Mellon University Pronouncing Dictionary~\citep{Weide98},\footnote{The CMU Pronouncing Dictionary is included in the NTLK package~\citep{Bird09}, the natural language processing toolkit we used for the analysis.}
    \item The average \textbf{Number of Syllables} for all pronunciations of a word, also obtained from the CMU Pronouncing Dictionary,
    \item The \textbf{Number of Meanings} for a word, obtained from WordNet~\citep{WordNet10}. \rk{add ref on why it's important}
\end{itemize}

@@

\rk{Choose which figure to show (see garbage at the end of file)}

\rk{Once chosen, comment results and transition to micro process}

%\begin{figure*}[!th]
%    \centering
%    \includegraphics[width=\textwidth]{images/computed-figures/timebags_evolution.png}
%    \caption{\textbf{Feature distribution evolution:} evolution of the distribution of feature values in substitution chains over successive 2-day time bags (bags 0 to 18, i.e. days 0 to 39).
%    The legends indicate the number of words left in each time bag; these decrease exponentially since only a fraction of the quotes undergo substitution at each step.
%    After a period of time, each feature becomes concentrated in a specific range of its own.}
%    \label{fig:timebags-evolution}
%\end{figure*}

>>>>

\begin{itemize}
    \item \textbf{Word frequency}: the frequency at which words appear in our dataset, \rk{add ref on why it's important}
    \item \textbf{Age of Acquisition}: the average age at which words are learned, obtained from~\citet{kuperman12},
    \item The average \textbf{Number of Phonemes} for all pronunciations of a word, obtained from the Carnegie Mellon University Pronouncing Dictionary~\citep{Weide98},\footnote{The CMU Pronouncing Dictionary is included in the NTLK package~\citep{Bird09}, the natural language processing toolkit we used for the analysis.}
    \item The average \textbf{Number of Syllables} for all pronunciations of a word, also obtained from the CMU Pronouncing Dictionary,
    \item The average \textbf{Number of Synonyms} for all meanings of a word, obtained from WordNet~\citep{WordNet10}. \rk{add ref on why it's important}
\end{itemize}

@@

\rk{Comment results and transition to micro process}

\begin{figure*}[!tbh]
    \centering
    \includegraphics[width=\textwidth]{images/computed-figures/timebags_evolution_recursive_min20_no-exclusion.png}
    \caption{\textbf{Feature distribution evolution:} evolution of the distribution of feature values in substitution chains over successive 2-day time bags (bags 0 to 18, i.e. days 0 to 37).
    The legends indicate the number of words left in each time bag; these decrease exponentially since only a fraction of the quotes undergo substitution at each step.
    After a period of time, each feature becomes concentrated in a specific range of its own.}
    \label{fig:timebags-evolution}
\end{figure*}
